### 2015-07-07 narrative/placement.tex
some changes

%key points based on discussion with Carlos
%1. Allocation tables and simple search won't be able to scale
%2. Carlos suggests looking at a determinstic function to decide on
%placement of data into the storage hierarchy. Instead of storing the
%metadata that describes where data is stored (which server/tier) we can
%simple associate a function for each application. 
%3. Research into what would be an approrpriate function that allows even
%splitting of data across many servers/tiers
%4. Similar to our approach for defining utility over time
%5. Migration can also use a function. We shouldn't distinguish migration
%from data movement and placement too much
%6. We need metrics that can decide how the data moves up and down in the
%hierarchy (so we can enable pre-fetching)
%7. Carlos suggested that instead of hints we call them service level
%objectives (and that leads into quality of service)
The application workflows targeted in this proposal generate very large
amounts of data, which needs to be processed and analyzed before
potential insights from the simulations can be realized. 
In-situ and in-transit data staging approaches can alleviate some of the
burden on storage, leveraging available compute and memory resources on high
end systems to process the data close to where it is generated. 
However, given current architectural trends, emerging systems will have a
vastly great gulf between the computing capability (the capability to
generate data) and the storage capability (the capability to store the
generated data). Moreoever, the complexity and heterogeniety of the
architecture will introduce new tiers in the storage system. Instead of
being a flat, roughly homogenous space in which data can be stored, the new
storage hierarchy will be multi-tiered and greatly heterogeneous.

We address three main concerns for the data lifecycle in this work. First,
we will explore the initial placement of data during the output process.
Second, we will study techniques that can enhance migration without making
the eventual lookup of data unbounded. And finally, we will study how data
at each tier is managed. %FIXME

Towards this end, we will utilize the faster layer of the
storage hierarchies, such as DRAM, NVRAM and remote NVRAM, as the target for
the initial write from an application. To mitigate the space concerns, we
will use the techniques described in Section~\ref{sec:refactoring} to
identify and partition the segments of data with the highest utility for the
application and use case. The rest of the data will be stored on the
parallel file system, as is done today. We will leverage the supported data
mirgration techniques in \Sir to determine the most appropriate location to
move the data once its in stable storage. This migration will be guided by a
combination of the utility function defined by the application and the
resources avialable to the storage system. Knowing the specific structural
and semantic information (including relationships between data segments)
about the data will enable migration to partition the data further to
optimize access to data for reader. 
We will also explore policies that combine the knowledge of data, its
utility to users, the cost of maintaining data in long term storage and
other metrics to decide how to purge irrelevant data from the storage
system.

>>>>

%key points based on discussion with Carlos
%1. Allocation tables and simple search won't be able to scale
%2. Carlos suggests looking at a determinstic function to decide on
%placement of data into the storage hierarchy. Instead of storing the
%metadata that describes where data is stored (which server/tier) we can
%simple associate a function for each application. 
%3. Research into what would be an approrpriate function that allows even
%splitting of data across many servers/tiers
%4. Similar to our approach for defining utility over time
%5. Migration can also use a function. We shouldn't distinguish migration
%from data movement and placement too much
%6. We need metrics that can decide how the data moves up and down in the
%hierarchy (so we can enable pre-fetching)
%7. Carlos suggested that instead of hints we call them service level
%objectives (and that leads into quality of service)
The application workflows targeted in this proposal generate very large
amounts of data, which needs to be processed and analyzed before
potential insights from the simulations can be realized. 
In-situ and in-transit data staging approaches can alleviate some of the
burden on storage, leveraging available compute and memory resources on high
end systems to process the data close to where it is generated. 
However, given current architectural trends, emerging systems will have a
vastly great gulf between the computing capability (the capability to
generate data) and the storage capability (the capability to store the
generated data). Moreover, the complexity and heterogeneity of the
architecture will introduce new tiers in the storage system. Instead of
being a flat, roughly homogeneous space in which data can be stored, the new
storage hierarchy will be multi-tiered and greatly heterogeneous. 
%
We address three main concerns for the data life-cycle in this work. First,
we will {\it explore the initial placement} of data during the output process.
Second, we will study techniques that can {\it enhance migration} without making
the eventual lookup of data unbounded. And finally, we will study {\it manage each tier} in a scalable fashion. %FIXME

Towards this end, we will utilize the faster layer of the
storage hierarchies, such as DRAM and NVRAM as the target for
the initial write from an application. To mitigate the space concerns, we
will use the techniques described in \S~\ref{sec:data-refactor} to
identify and partition the segments of data with the highest utility for the
application and use case. The rest of the data will be stored on the
lower layers of the file system, such as the parallel file system, as is done today. 
We will leverage the supported data
migration techniques in \Sir~to determine the most appropriate location to
move the data once its in stable storage. This migration will be guided by a
combination of the utility function defined by the application and the
resources available to the storage system. Knowing the specific structural
and semantic information (including relationships between data segments)
about the data will enable migration to partition the data further to
optimize access to data for reader. For example, in Fig.~\ref{fig:ssio-bucket},
P3 is initially placed in Campaign storage, since it's size and utility allow our system
to place data there, but as the utility of data allows this chunk to be migrated to the 
Long Term, and slower, storage layer to allow other data chunks from other users to take advantage
of this space. Similar, P2 migrates from the Parallel FS to Campaign storage to clear room for other
users. We will utilize this migration and eviction strategy for Checkpoint/Restart (C/R) data as well, 
where data can be initially placed on NVRAM and then purged after the next (or next two) C/R files
are written to NVRAM.

We will also explore policies that combine the knowledge of data, its
utility to users, the cost of maintaining data in long term storage and
other metrics to decide how to purge irrelevant data from the storage
system.
